---
title: "Exploration of the USDA Data Set"
author: "Andrea Argueta, Mariam Khan, Brynna Kilcline, and William Zhang"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r include=FALSE}
library(knitr)
library(leaflet)
library(htmltools)
library(plotly)
library(dplyr)
library(ggplot2)
library(maps)
source("scripts/map.R")
source("scripts/production.R")
source("scripts/summ_table .R")
source("scripts/summ_info.R")
source("scripts/exports.R")

df <- read.csv("data/coffee_df.csv", stringsAsFactors = FALSE)
```

While the world seems to be in a standstill, we thought we would choose an aspect of many people's lives that serves as a constant: coffee. Coffee is a bridge for people to connect, so looking into it further to see who/where experiences coffee in different ways is very interesting to our group. Our goal is that through this project we want to understand how the global consumption differs across countries and over time. 

The United States Department of Agriculture (USDA) collects data from agency activities which are then summarized into reports. The file we are going to explore consists of data about coffee bean production, export, import and consumption for every country by year. With this data, we can answer our questions about how coffee production and coffee culture is distributed around the world.

## Summary Information
```{r, echo=FALSE}
list <- summ_info(df)
```
In 2019, `r list[[3]]` countries and republics exported/imported coffee. During the year, `r list[[2]]` thousand bags (each weighing 60kg) of beans were imported globally. Likewise, `r list[[1]]` thousand bags were exported worldwide. Also, `r list[[4]]` thousand bags of Arabica coffee were produced amongst the countries in the summary table. Domestic consumption totalled to `r list[[5]]` thousand bags in the year 2019.

## Summary Table
```{r, echo=FALSE}
kable(summ_table(df))
```

## Map of Coffee Consumption

This chart visualizes domestic coffee consumption for countries in 2019. Domestic consumption refers to the amount that was imported or produced and not exported. Population size is not taken into account. The visualization can help us understand the total amount of coffee consumed by each country last year.
```{r fig.width=15, fig.height=8, echo=F}
create_map(df)
```

From this, we can see that Europe, the United States, and Brazil consumed large amounts of coffee. This makes sense given the size of their populations. In contrast, the total consumption in individual African countries was minimal.

## Trend Line of Coffee Production 

This chart visualizes the global production of coffee from the year 1961 to 2019. This production value is measured in 1000 bags of coffee, with each bag weighing at 60kg.This value also accounts for all forms of produced coffee products including coffee beans, ground coffee and soluble coffee.
```{r, echo=F}
product_year_f(df)
```
From this, we can see that the global production of coffee has almost tripled from 1961 to 2019. The global production of coffee grew from 65,341 to 174,640 (1000 60kg bags) in 57 years. Although not shown in the chart, Brazil is the leading producer of coffee in every year.

## Bar Graph of Coffee Exports

The chart below visualizes the amount of coffee exported by the the top five exporting countries since 2010 (Brazil, Columbia, Vietnam, Indonesia, and Honduras). The top five were found by the filtering to the countries of the top 150 amounts of coffee exported in the last ten years.

```{r, echo=F}
create_exports_chart(df)
```

From this chart, we can see that Brazil is the leading country in coffee exports in the past ten years. It is visible that Brazil exported over twice the amount that Vietnam has. We can also see that Vietnam and Columbia come in a close second. 

